% ABSTRACT--------------------------------------------------------------------------------

\begin{resumo}[ABSTRACT]
\begin{SingleSpacing}

% Não altere esta seção do texto--------------------------------------------------------
\imprimirautorcitacao. \imprimirtitleabstract. \imprimirdata. \pageref {LastPage} f. \imprimirprojeto\ – \imprimirprograma, \imprimirinstituicao. \imprimirlocal, \imprimirdata.\\
%---------------------------------------------------------------------------------------

The present proposal refers to the development of an application for calculating soil balance and correction. An application will be developed with the agile development technique, TDD and will be modeled with UML diagrams, which will provide a view about functionalities, class organization and deployment, in addition to providing the view of the database model with DER. The development will be based mainly on PHP and JavaScript programming languages, being Laravel the PHP framework to backend and React the JavaScript library to frontend development, toghetter with Ant Design for React, besides to MySQL using the DBMS. Codeception will be the framework to write and execute automated tests on the red and green steps of TDD. The Git will be used as a code repository and will be hosted on GitHub. The tasks management will be make with Trello, that provides an view about the project development status, using the kanban concept.

\textbf{Keywords}: Soil correction and balance. System development. Web development.

\end{SingleSpacing}
\end{resumo}

% OBSERVAÇÕES---------------------------------------------------------------------------
% Altere o texto inserindo o Abstract do seu trabalho.
% Escolha de 3 a 5 palavras ou termos que descrevam bem o seu trabalho 
